---
title: 'Table of Contents'
date: ""
author: ""
output:
  html_document:
    theme: cerulean
    toc: yes
---

### Description
Individual subject data and R code to reproduce data analysis and figures reported in "Low intensity TMS enhances perception of visual stimuli" by Arman Abrahamyan, Colin Clifford, Ehsan Arabzadeh and Justin Harris. 

```{r echo=FALSE, message=FALSE}
library(ggplot2)
library(ggthemes)
## Load Winston Chan's function to compute within-subjects error bars
source('~/Desktop/Dropbox/R/Lib/StandardErrorsByWinstonChan.R')
setwd("~/Desktop/Dropbox/Work/USyd/Experiments/OrientationDiscrimination_LowTMS/OrientationExp_DataAnalysis_R/")

# Load data and display loaded variable
load("Exp1_Exp2.RData", verbose=T)
#head(Exp1_Exp2)
# Compute visual sensitivity, which is reciprocal of contrast threshold
exp1_data <- ddply(exp1_data, .(PPT, Date, Condition), transform, Sensitivity=1/Th)
exp2_data <- ddply(exp2_data, .(PPT, Date, Condition), transform, Sensitivity=1/Th)
```



```{r}
summary(cars)
```

You can also embed plots, for example:

```{r, echo=FALSE}
plot(cars)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
